Cybercrime and Online Video Games

### 2019-12-14 paper/paper.tex
Expand fortnite section

\subsection{Fortnite: Battle Royale}
Developed by Epic Games, "Fortnite: Battle Royale" or "Fortnite" is a 
third-person shooter and battle royale online video game. The player must
utilize a diverse arsenal of weapons to defeat 99 other human opponents and 
claim victory.

>>>>

\subsection{Fortnite: Battle Royale}
Developed by Epic Games, "Fortnite: Battle Royale" or "Fortnite" is a 
third-person shooter and battle royale online video game. The player must
utilize a diverse arsenal of weapons to defeat 99 other human opponents and 
claim victory. Initially, the players compete in a strikingly large play area.
But as time elapses in the match, the size of the arena shrinks gradually. As a
result, players will more easily combat each other in the ultimate goal of 
surviving all other players. Fortnite is unique from video games like "Call of 
Duty"  how it handles player progression. In the "Call of Duty" franchise of
video games, as players defeat opponents, they earn "experience" which unlocks "levels" of
progression. These levels unlock new weapons and abilities to enable the player 
to intesify their customization to match the player's interests and desires. By
comparison, at the beginning of a Fortnite match, all players start with the
same, mediocre weapon and are tasked with exploring the gameplay arena for 
improved equipment. Therefore, it is impossible for players to purchase an
advantage that affects their gameplay, which raises the question of how 
Fortnite generates revenue for Epic Games. Fortnite is a free-to-play video game, which means that there is
no initial upfront cost to downloading and playing the game; however, Epic Games
has monetized the game through the availablity of a store for cosmetic items. 
These cosmetic items can only be acquired by purchasing "V-Bucks" from Epic Games.
Cosmetic items - as the name might imply - modify the external appearance of the 
player's avatar in a Fortnite match. Cosmetics are sometimes exclusive to 
certain accomplishments and time periods. Because of this, an account with 
a large collection of cosmetic items can easily have a real-world currency value
associated with it. And for exclusive items, the rarity and inability to 
earn these items as a later player means that these accounts are valuable. The 
combination of exciting, fast-paced matches and unique ways to customize one's
character avatar has helped to make Fortnite one of the most popular video games
ever.

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{DistributionFortniteAge.png}
	\caption{Fortnite Age Distribution}
\end{figure}
